 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-07-17 paper.Rmd
update text

To begin we look at simulated datasets that reproduce known facts
aboutthe  t-SNE algorithm. Our first data set consists of five spherical 5-$d$
Gaussian clusters embedded in 10-$d$ space, each cluster has the same 
covariance matrix. We then computed a t-SNE layout using default settings,
and set up the `liminal` linked interface with grand tour on the 10-$d$
observations (video - ).

@@

Moreover, we run t-SNE using the default arguments on the complete data (this
keeps the first 50 PCs, sets the perplexity to equal 30 and performs random
initialisation) using the `Rtsne` package [@Rtsne]. We then create a linked
tour with t-SNE layout with `liminal` as shown in the following video :

>>>>

To begin we look at simulated datasets that reproduce known facts
aboutthe  t-SNE algorithm. Our first data set consists of five spherical 5-$d$
Gaussian clusters embedded in 10-$d$ space, each cluster has the same 
covariance matrix. We then computed a t-SNE layout with default settings 
using the `Rtsne` package [@Rtsne],
and set up the `liminal` linked interface with grand tour on the 10-$d$
observations (video - ).

@@

Moreover, we run t-SNE using the default arguments on the complete data (this
keeps the first 50 PCs, sets the perplexity to equal 30 and performs random
initialisation). We then create a linked
tour with t-SNE layout with `liminal` as shown in the following video :
